Learning Auditory Similarities Between Instrumental Playing Techniques

### 2019-10-31 paper/paper.tex
lower case
address JA's comments re named section

Following the above discussed matters, we propose a ranking system that is based on a processing pipeline made of two main components, see Figure \ref{fig:pipeline}.
The first component maps the audio signal of the query and the items of the database into a high-dimensional timbre space using the scattering transform.
The second component warps this timbre space by taking into account perceptual judgments represented as a consensus clustering of the items in the dataset, as presented in Section \ref{sec:survey}.
This warping, or reweighting, of the space is performed using LMNN.
\ja{Again, section numbers are not showing up here.}%

>>>>

Following the above discussed matters, we propose a ranking system that is based on a processing pipeline made of two main components, see Figure \ref{fig:pipeline}.
The first component maps the audio signal of the query and the items of the database into a high-dimensional timbre space using the scattering transform.
The second component warps this timbre space by taking into account perceptual judgments represented as a consensus clustering of the items in the dataset, as presented in the \nameref{sec:survey} section.
This warping, or reweighting, of the space is performed using LMNN.
